%-------------------------------------------------------------------------------
%    SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%    CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Just Eat Takeaway} % Organization
    {Amsterdam, Netherlands} % Location
    {Aug. 2021 -- Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architected and developed financial systems including a Double Entry/General Ledger platform capable of handling millions of transactions daily.}
        \item {Led development of distributed, highly scalable services using microservices architecture.}
        \item {Provided technical leadership in architectural design, code quality, and infrastructure decisions.}
        \item {Worked with technologies such as Java, Kotlin, Spring, C\#, .NET, AWS, Postgres, MySQL, Apache Kafka, Kubernetes, Grafana, Datadog, and Vault.}
        \item {Actively contributed to internal knowledge sharing, mentoring, and codebase improvements.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Backend Software Engineer} % Job title
    {iFood} % Organization
    {São Paulo, Brazil} % Location
    {Aug. 2021 -- Aug. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked at one of the largest tech companies in LATAM, supporting millions of users.}
        \item {Designed and built highly scalable distributed systems for financial and credit operations.}
        \item {Developed a Double Entry/General Ledger system to process millions of transactions daily.}
        \item {Contributed to product development, architectural design, and technical leadership.}
        \item {Technologies included Java, Kotlin, Spring, NodeJS, NestJS, AWS, Postgres, Apache Kafka, Kubernetes, Grafana, NewRelic, Vault.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Backend Software Engineer (Mid-level/Senior)}
    {Looqbox}
    {Campinas, Brazil}
    {Jul. 2020 -- Aug. 2021}
    {
      \begin{cvitems}
        \item {Led key projects and conducted technical interviews to support team growth and hiring at a high-potential startup (100 Startups to Watch Brazil).}
        \item {Designed and deployed NLP and web services used by tens of thousands of active users.}
        \item {Implemented microservices architecture with REST APIs, CI/CD pipelines, and message brokers for scalable backend systems.}
        \item {Utilized Java, Kotlin, Spring, Redis, RabbitMQ, MongoDB, Elasticsearch, GCP, Apache Beam, and Kubernetes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Engineer}
    {Dextra}
    {Campinas, Brazil}
    {Jan. 2020 -- Jun. 2020}
    {
      \begin{cvitems}
        \item {Architected and implemented distributed data processing pipelines (batch and streaming) for a multinational financial client.}
        \item {Achieved high throughput and low-latency performance using parallel processing and clustered computing.}
        \item {Tech stack included Scala, Python, Apache Spark, Kafka, and Parquet.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer}
    {Samsung's Institute of Research and Development}
    {Campinas, Brazil}
    {Oct. 2018 -- Oct. 2019}
    {
      \begin{cvitems}
        \item {Contributed to the development and localization of Bixby (Samsung’s voice assistant) for the Portuguese language, launched in 2020.}
        \item {Collaborated with international teams to ensure integration and quality across different regions and platforms.}
        \item {Also developed IoT features for Samsung’s Family Hub refrigerator line.}
        \item {Worked primarily with Java, Android, and JavaScript.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
